\section{Preface}

\subsection{My work}

I'm working at Imperia AG\footnote{http://www.imperia-ag.com} since August 2003.
I began as a trainee in software development and succeeded after 2 1/2 years.
I'm in the product development of our content management system.
Until about 2005 most of my work was just programming new features and fixing my bugs.
Then two other ex-trainee's and myself were selected to do third level support additionally to our usual work.
So I got more and more into analysis of problems and therefore also JVM specific analytic methods, like thread and heap dumps.
At the moment I'm mostly writing frontend code and analysing problems, so I need something to work at which doesn't have anything to do with frontend ;)

\subsection{My problems}

An ex-co-worker, Ingo Rockel\footnote{http://www.grimmfrost.de}, did much analytic stuff too.
He wrote a tool called thread dump analyzer (TDA)\footnote{https://tda.dev.java.net/}.
The tool is graphical oriented and helped me a lot to analyze thread dumps.
But after looking at thread dumps for over three years now I found out that many common things repeat.
In application server environments, like ours, you just need to look at a couple of thread types, like request threads to quickly see what the problem was, if it's a problem that can be analysed by thread dumps.
Also things like hanging jdbc connections may be common.
So I wanted to reduce the time I need to check these common problems.
A frontend tool isn't very suitable for this type of work, so the answer must be a command line tool which can be used through scripts.

\subsection{My solution}

To achieve this automatism I began writing the jtdutils.
A set of atomar tools which can be combined very flexible to enable powerful scripts.

\subsection{My intentions}

When I thought about this project I had to decide which language to take.
I'm doing java over six years now. 
So this is no option.
A script language?
Maybe...
C/C++?
Sounds good, but C or C++? Hm. This took me quite some time, but in the end I decided for C because I don't like the style of C++.
